Critical assessment of Linear-Response Excitations in Molecular system\\ or \\ On the Localization of the Linear-Response excitations in Open Systems

### 2017-12-27 LRDraft.tex
updatte

We introduce the excitonic states defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
coefficients that appears in \eqref{XYcoeffDef1}, that is:
\begin{align}
\ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
\tbra{\phi^E_p} &\equiv \sint \dd \alpha {\tilde X_{E}^{p \alpha}} \bra{\psi(\alpha)} \;, \nn\\
\bra{\chi^E_p} &\equiv \sint \dd \alpha  Y_{E}^{p \alpha} \bra{\psi(\alpha)} &
\tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;.
\end{align}
Thanks to these definitions we can express the excitation operators as follows:
\be
\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
\op {\tilde E} = \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
\ee
The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated in Schroedinger-like equations
for the excitonic states.

>>>>

We introduce the excitonic states defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
coefficients that appears in \eqref{XYcoeffDef1}, that is:
\begin{align}
\ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
\tbra{\phi^E_p} &\equiv \sint \dd \alpha {\tilde X_{E}^{p \alpha}} \bra{\psi(\alpha)} \;, \nn\\
\bra{\chi^E_p} &\equiv \sint \dd \alpha  Y_{E}^{p \alpha} \bra{\psi(\alpha)} &
\tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;.
\end{align}
Thanks to these definitions we can express the excitation operators as follows:
\be\lb{ExctitationOperatorsDef2}
\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
\op {\tilde E} = \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
\ee
The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated in Schroedinger-like equations
for the excitonic states.

\vspace{0.5cm}
\emph{Solution for $\coupl = 0$}
\vspace{0.5cm}

\noindent In this case the $\optr{L}_{q\beta}^{p\alpha}$ matrix has only diagonal non-vanishing elements, given by: 
\be
\trace{\decay{\alpha}{p}\Liouv\excite{q}{\beta}} = H_{0\alpha\beta}\delta_{pq} - \eps_p\delta_{pq}\delta(\alpha-\beta) \;, \qq
\trace{\excite{\alpha}{p}\Liouv\decay{q}{\beta}} = \eps_p\delta_{pq}\delta(\alpha-\beta) - H_{0\beta\alpha}\delta_{pq} \;, 
\ee
where $H_{0\alpha\beta} = \bra{\psi(\alpha)}\hnot\ket{\psi(\beta)}$. The eigenvalue conditions \eqref{LiouvMatrixEigenvectorDef1} imply
that the $Y$ and $\tilde Y$ coefficients introduced in \eqref{XYcoeffDef1} vanish so that both $\tket{\chi^E_p}$ and $\bra{\chi^E_p}$ do not
contribute to the excitation operators \eqref{ExctitationOperatorsDef2}. The eigenvalue operator equation for $\op E$ reduces to:
\be
\sum_q\left(\hnot - \eps_q\right)\ket{\phi^E_q}\bra{\psi_q} = E \sum_q \ket{\phi^E_q}\bra{\psi_q} \;,
\ee
and projecting on $\ket{\psi_q}$ provides the eigenvalue condition for the excitonic $\ket{\phi^E_p}$ state:
\be
\left(\hnot - \eps_p\right)\ket{\phi^E_p} = E \ket{\phi^E_p} \;.
\ee
In the same way we can derive an analogous equation for $\tbra{\phi^E_p}$ by using the eigenvalue condition for $\op{\tilde E}$. To achieve this
result we need the expression of the left action of the (unperturbed) Liouville superoperator defined in \eqref{L0sopDef1}, that can be derived by
observing that:
\be
\trace{\op O' (\Liouvnot \op O)} = \trace{(\op O' \Liouvnot) \op O } =
\trace{\commutator{\op O'}{\op H_0} \op O} \quad \Rightarrow \quad \op O \Liouvnot = 
- \Liouvnot \op O \;.
\ee
So, the eigenvalue operator equation for $\op{\tilde E}$ provides:
\be
\sum_q  \ket{\psi_q} \tbra{\phi^E_q} \left( \hnot - \eps_q \right) =
E \sum_q  \ket{\psi_q} \tbra{\phi^E_q} \;,
\ee
so that:
\be
\tbra{\phi^E_p} \left( \hnot - \eps_p \right) = E \tbra{\phi^E_p} \;.
\ee
In other terms we find that the perturbation states must be left and right eigenvectors of  $\hnot$.

The operators $\op E$ and $\op{\tilde E}$ have an important physical meaning:
if they are used as perturbation operators they would generate a response density 
with a well-defined energy:
\be
\commutator{\op E}{\dmnot} = E \;, \qquad \commutator{\op{\tilde E}}{\dmnot} = -\op{\tilde E}
\ee
The above equations show that we would have, respectively:
\be
\dm'(\omega) = \frac{1}{\bbomega - E} \op E\;,\qquad
\dm'(\omega) = \frac{1}{\bbomega + E} \op{\tilde E}
\ee
In other terms, they constitute the \emph{resonant channels} of the excitation of the
density. The decomposition of the perturbation operator $\op \Phi$ among these channels
would provide $\dm'(\omega)$.
